CFRD Screening Survey

### 2022-04-07 Christine Chan/CFRD Screening Survey/cfrd_screening_analysis.Rmd
CFRD screening proportions

plot_df = data.frame(rbind(endo_alt,non_endo_alt))
t = plot_df %>% pivot_wider(id_cols = name,values_from = n,names_from = type) %>%
  column_to_rownames(.,var = "name")
# Plot
ggplot(plot_df,aes(x = name,y = n,group = type,fill = type)) + 
  geom_bar(stat="identity",position=position_dodge()) +
  theme_bw() + theme(legend.title = element_blank()) + 
  xlab("Other Diabetes Screening Methods")
```

>>>>

plot_df = data.frame(rbind(endo_alt,non_endo_alt))
t = plot_df %>% pivot_wider(id_cols = name,values_from = n,names_from = type) %>%
  column_to_rownames(.,var = "name")

```

### Percentages by responder type

```{r}
# Table
kable(proportions(data.matrix(t),margin = 2)*100,digits = 2)
```

### Figure

```{r}
# Plot
ggplot(plot_df,aes(x = name,y = n,group = type,fill = type)) + 
  geom_bar(stat="identity",position=position_dodge()) +
  theme_bw() + theme(legend.title = element_blank()) + 
  xlab("Other Diabetes Screening Methods")
```
